EE454 Project 1 Report

### 2015-09-23 p1/report/latex/draft.tex
continued discussion in intermediate output

Included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.

@@

		Accuracy = 43.7\%
\end{center}

>>>>

Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.  The images can be produced by running `demo.m.'

Observation of the output from each layer is consistent with the project description.  Normalization produces an image with scaled pixel values but is relatively unchanged.  Convolution produces a set of images with different feature sets extracted.  The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).  Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.  Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.

@@

		\textbf{Accuracy = 43.7\%}
\end{center}
